Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-13 paper/reviewers-response.Rmd

> I think the concepts presented in this manuscript are a useful addition to the literature on management of ecological networks.  I agree with the authors that it is important that the discussion surrounding what constitutes a "keystone" species should go beyond centrality metrics.

> I found the results and concepts to be generally well presented, particularly graphically, and the authors present a thorough sensitivity analysis to various assumptions.  The methods are mostly clear but there is no description of how the "likelihood of being a superior node " is calculated.

> I would suggest including clarification on the limitations of using control capacity to summarise species' importance, and examples to help the reader build an intuition regarding the control capacity metric.  As pointed out, networks that give rise to a species having a high control capacity can be quite distinct to networks that give rise to a species having a high value of particular centrality metrics.  Providing an example in the Discussion of, for instance, those species that have a control capacity of 1 but a low degree would be very useful.

> "*Discussion*: 'species' strength'

*Accepted and changed*: In the Methods section we deine species' strength as the sum of a species' visits (\lr{M-R2-species-strength-a}). For brevity, we did not define it again in the Disussion, but now we have improved the text and briefly describe it when we mention it there too. The text now reads "When controlling for a species' visitation strength (the sum of a species' visits), which is indirectly a proxy of its abundance..." (\lr{M-R2-species-strength-b}).

### 2019-01-13 paper/manuscript.Rmd
Clarify usage of species strength in the discussion

\R{R2-one-lumped-model-a}We then examined how species-level properties were related to control capacity using a set of candidate generalised linear models with binomial error structure. 
These models included five predictor variables that mirror the network-level predictors. 
First, the species' contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
Second, the species' strength (the sum of a species' visits), which quantifies the strength of a species' associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
Third, the direction of asymmetry which quantifies the net balance in dependencies; that is, it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007]. 
Fourth, the species' degree in order to account for the intrinsic centrality of a species.
Finally, we included a categorical variable for the species' trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one.
\R{R2-one-lumped-model-b}In these models, species from all networks were lumped together. 
To identify the models that were best supported by the data, we first determined the most parsimonious random structure using the AICc. 
The relative importance of variables was then assessed by looking at their effect sizes in the top-ranked models and the cumulative weight of the models in which they are present.

@@

When controlling for a species' strength, which is indirectly a proxy of its abundance, and the net balance of its dependencies, we found that control capacity could not be easily predicted by species' degree or other metrics of centrality.
For instance, some species with a low degree achieved the maximum control capacity and were critical for control in their communities. 
At first glance, our findings challenge numerous studies that highlight the role that central species play in the dynamics of their communities and their utility at predicting species extinctions [@jordan_keystone_2009]. 
However, further inspection shows that our results do not contradict these findings; most species with a large degree also have a large control capacity and all of them were classified as superior nodes which corroborates the utility of classic centrality metrics. 
Putting these observations together, our results therefore take previous findings one step further and suggest that centrality might paint an incomplete picture of the relevance of species.

>>>>

\R{R2-one-lumped-model-a}We then examined how species-level properties were related to control capacity using a set of candidate generalised linear models with binomial error structure. 
These models included five predictor variables that mirror the network-level predictors. 
First, the species' contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
Second,\R{R2-species-strength-a} the species' strength (the sum of a species' visits), which quantifies the strength of a species' associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
Third, the direction of asymmetry which quantifies the net balance in dependencies; that is, it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007]. 
Fourth, the species' degree in order to account for the intrinsic centrality of a species.
Finally, we included a categorical variable for the species' trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one.
\R{R2-one-lumped-model-b}In these models, species from all networks were lumped together. 
To identify the models that were best supported by the data, we first determined the most parsimonious random structure using the AICc. 
The relative importance of variables was then assessed by looking at their effect sizes in the top-ranked models and the cumulative weight of the models in which they are present.

@@

When controlling for a \R{R2-species-strength-b}species' visitation strength (the sum of a species' visits), which is indirectly a proxy of its abundance, and the net balance of its dependencies, we found that control capacity could not be easily predicted by species' degree or other metrics of centrality.
For instance, some species with a low degree achieved the maximum control capacity and were critical for control in their communities. 
At first glance, our findings challenge numerous studies that highlight the role that central species play in the dynamics of their communities and their utility at predicting species extinctions [@jordan_keystone_2009]. 
However, further inspection shows that our results do not contradict these findings; most species with a large degree also have a large control capacity and all of them were classified as superior nodes which corroborates the utility of classic centrality metrics. 
Putting these observations together, our results therefore take previous findings one step further and suggest that centrality might paint an incomplete picture of the relevance of species.
